---
title: "Guess (two)"
author: "Julian Ricardo"
date: "`r Sys.Date()`"
output: 
  html_document:
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyr)
library(forcats)
library(ggplot2)
library(scales)
library(patchwork)
library(ggbeeswarm)
library(ggalt)
library(colorspace)

theme_set(theme_minimal() +
            theme(panel.grid.minor = element_blank(),
                  panel.grid.major.x = element_blank()))

source(here::here("R", "load_guess.R"))
```

AgeGuess.org is a simple on-line game using biological and perceived age as biomarkers to address scientific questions related to aging in humans. The AgeGuess project updates the AgeGuess.org Public Data Set every three months.

Aim for part two is to compare how guesses do depending on match (or not) b/w gender, ethnicity, birth county, and age between guesser AND photo

```{r}
mad_calc <- ag_guess_ethn_match %>% 
  .[, list(.N,
           mad = mad(outG),
           median = as.double(median(abs(outG))),
           mean = mean(abs(outG)),
           sd = sd(outG)),
    by = "match_ethnicity"] %>% 
  .[, cv_mad := mad/median] %>% 
  .[, cv_mean := sd/mean]

mad_calc2 <- ag_guess_ethn_match %>% 
  .[, list(.N,
           mad = mad(outG),
           median = as.double(median(abs(outG))),
           mean = mean(abs(outG)),
           sd = sd(outG)),
    by = c("match_ethnicity", "ethnicity")] %>% 
  .[, cv_mad := mad/median] %>% 
  .[, cv_mean := sd/mean]
```


```{r}
ag_guess_ethn_match %>% 
  .[, c("ageT", "outG", "match_ethnicity")] %>% 
  .[, match_ethnicity := fct_relevel(as.character(match_ethnicity),
                                     "TRUE", "FALSE")] %>% 
  .[, decade := factor(floor(ageT/10)*10)] %>% 
  ggplot(aes(x = decade)) +
  stat_summary(
    mapping = aes(y = outG, 
                  color = match_ethnicity),
    fun.ymin = function(z) { quantile(z,0.25) },
    fun.ymax = function(z) { quantile(z,0.75) },
    fun.y = median,
    position = position_dodge(width = 0.618),
    size = rel(1.05)) +
  scale_color_discrete_qualitative("Cold") +
  labs(x = "Age", y = "Error in guess", color = NULL) +
  theme(legend.position = c(0.25, 0.25),
        legend.direction = "horizontal")

ag_guess_ethn_match %>% 
  .[, c("ageT", "outG", "ethnicity", "match_ethnicity")] %>% 
  .[, match_ethnicity := fct_relevel(as.character(match_ethnicity),
                                     "TRUE", "FALSE")] %>% 
  .[, ethnicity := fct_infreq(ethnicity) %>% 
      fct_relevel("Not specified", after = Inf)] %>% 
  .[, decade := factor(floor(ageT/10)*10)] %>% 
  ggplot(aes(x = decade)) +
  stat_summary(
    mapping = aes(y = outG, 
                  color = match_ethnicity),
    fun.ymin = function(z) { quantile(z,0.25) },
    fun.ymax = function(z) { quantile(z,0.75) },
    fun.y = median,
    position = position_dodge(width = 0.618)) +
  facet_wrap( ~ ethnicity) +
  scale_color_discrete_qualitative("Cold") +
  labs(x = "Age", y = "Error in guess", color = NULL) +
  theme(legend.position = "bottom",
        legend.direction = "horizontal")
```
